Preprocessing summary

### 2016-03-26 inst/examples/summary.Rmd
ok

---
title: "Summary"
author: "Leo Lahti and Niko Ilomäki"
date: "Feb 24, 2016"
output: markdown_document
---

@@

# Read the preprocessed data
df <- readRDS("df.Rds")
df.orig <- readRDS("df.orig.Rds")
```

>>>>

---
title: "Preprocessing summary"
author: "Leo Lahti and Niko Ilomäki"
date: "March 2, 2016"
---

@@

# Read the preprocessed data
df <- readRDS("df.Rds")
df.orig <- readRDS("df.orig.Rds")
conversions <- readRDS("conversions.Rds")
```
